Community Data Science meets Digital Heritage: Controversies about World Heritage Sites in the Online Community of Wikipedia

### 2019-03-30 code/paper.Rmd
anomaly analysis

```{r}
randoms_revision_history_page_details_ip_location_props_per_page <- 
randoms_revision_history_page_details_ip_location %>% 
  filter(!is.na(country_name)) %>% 
  mutate(country_name = fct_rev(fct_infreq(country_name))) %>% 
  group_by(page, country_name) %>% 
  tally() %>% 
  mutate(prop = n / sum(n)) 
  filter(country_name %in% randoms_revision_history_page_details_ip_location_tally$country_name)

@@

can we identify a cluster of controversial pages? Not really

randoms_revision_history_page_details_ip_warring_words_prop_clus <- 
randoms_revision_history_page_details_ip_warring_words_prop %>% 
  left_join(ten_k_random_wp_pages %>% 
  mutate(page = 1:nrow(.))) %>% 
  select(rh_revert_prop, 
         prop_warring_edits,
         rh_diff_size_cv) %>%
   filter_all(all_vars(!is.na(.))) %>% 
  princomp(., scale = TRUE)

@@

randoms_revision_history_page_details_ip_time_diffs %>% 
  filter(!is.na(time_diff_hours)) %>% 
  mutate(quick_three_edits = time_diff_hours + lag(time_diff_hours) + lag(time_diff_hours, 2) + lag(time_diff_hours, 3)) %>% View

@@

randoms_revision_history_page_details_ip_time_diffs %>% 
  bind_cols(rle_tbl2) %>% 
  filter(lths2 == 1) %>% 
  filter(time_diff_hours < 24) %>% View

@@

>>>>

```{r}
randoms_revision_history_page_details_ip_location_props_per_page <- 
randoms_revision_history_page_details_ip_location %>% 
  filter(!is.na(country_name)) %>% 
  mutate(country_name = fct_rev(fct_infreq(country_name))) %>% 
  group_by(page, country_name) %>% 
  tally() %>% 
  mutate(prop = n / sum(n)) %>% 
  filter(country_name %in% randoms_revision_history_page_details_ip_location_tally$country_name)

@@

@@

randoms_revision_history_page_details_ip_time_diffs %>% 
  filter(!is.na(time_diff_hours)) %>% 
  mutate(quick_three_edits = time_diff_hours + lag(time_diff_hours) + lag(time_diff_hours, 2) + lag(time_diff_hours, 3))

@@

randoms_revision_history_page_details_ip_time_diffs %>% 
  bind_cols(rle_tbl2) %>% 
  filter(lths2 == 1) %>% 
  filter(time_diff_hours < 24)

@@

Spike detection

for randoms, what even is an anomaly?

```{r}
# devtools::install_github("hrbrmstr/AnomalyDetection")
library(AnomalyDetection)
randoms_revision_history_page_details_ip_location_monthly <- 
randoms_revision_history_page_details_ip_location %>% 
  group_by(page) %>% 
  mutate(the_d = floor_date(rh_date, "day")) %>% 
    mutate(the_m = floor_date(rh_date, "month")) %>% 
  group_by(page, the_m) %>% 
  tally() %>% 
  filter(n() > 150) # explore this value

randoms_revision_history_page_details_ip_location_monthly_anom <- 
  randoms_revision_history_page_details_ip_location_monthly %>% 
  ungroup %>% 
  group_nest(page) %>% 
  mutate(anomalies = map(data, ~ad_ts(.x, 
                                      max_anoms = 0.2, 
                                      alpha = 0.005,
                                      threshold = "p95"))) %>% 
  unnest(anomalies)

ggplot() +
  geom_line(
    data=randoms_revision_history_page_details_ip_location_monthly %>% 
      filter(page %in% randoms_revision_history_page_details_ip_location_monthly_anom$page), 
    aes(the_m, n), 
    size=0.125, color="lightslategray")  +
  geom_point(
    data=randoms_revision_history_page_details_ip_location_monthly_anom, 
    aes(timestamp, anoms), 
    color="#cb181d", alpha=1/3) +
  scale_x_datetime(date_labels="%b\n%Y") +
  facet_wrap( ~ page, scales = "free_y")

for WH sites

```{r}
revision_history_page_details_ip_addresses_df_monthly_edits <- 
revision_history_page_details_ip_addresses_df  %>% 
  mutate(the_d = floor_date(rh_date, "day")) %>% 
    mutate(the_m = floor_date(rh_date, "month")) %>% 
  group_by(Site, the_m) %>% 
  tally() %>% 
  filter(n() > 24) # explore this value

# distribution of edits per month
ggplot(revision_history_page_details_ip_addresses_df_monthly_edits,
       aes(n)) +
  geom_histogram() +
  scale_x_log10()

# subset so we get only sites with > 10 edits/month
revision_history_page_details_ip_addresses_df_monthly_edits_10 <- 
revision_history_page_details_ip_addresses_df_monthly_edits %>% 
  filter(max(n) >= 10)

# detect anomalies
revision_history_page_details_ip_addresses_df_monthly_edits_anoms <- 
  revision_history_page_details_ip_addresses_df_monthly_edits_10 %>% 
  ungroup %>% 
  group_nest(Site) %>% 
  mutate(anomalies = map(data, ~ad_ts(.x, 
                                      max_anoms = 0.2, 
                                      alpha = 0.005,
                                      threshold = "p95"))) %>% 
  unnest(anomalies) %>% 
  group_by(Site) %>% 
  filter(max(anoms) >= 50) # where the anomaly is 50 edits/month or more

ggplot() +
  geom_line(
    data=revision_history_page_details_ip_addresses_df_monthly_edits_10 %>% 
      filter(Site %in% revision_history_page_details_ip_addresses_df_monthly_edits_anoms$Site), 
    aes(the_m, n), 
    size=0.125, color="lightslategray")  +
  geom_point(
    data=revision_history_page_details_ip_addresses_df_monthly_edits_anoms, 
    aes(timestamp, anoms), 
    color="#cb181d", alpha=1/3) +
  scale_x_datetime(date_labels="%b\n%Y") +
  facet_wrap( ~ Site, scales = "free")
```
